A Survey of Quantitative Descriptions of Molecular Structure

### 2012-05-18 paper.tex
Added the new screenshots to the chapter

In addition to libraries and their wrappers there are various GUI
applications that allow easy descriptor calculations. Examples include
Bioclipse \cite{Spjuth:2007aa}, MOE (Chemical Computing Group) and
Maestro (Schr\"{o}dinger, Inc.). Workflow tools are also a useful
class of applications for descriptor generation and allow one to
easily generate descriptors from multiple sources~\cite{Truszkowski2011}. Given the focus of
this article on Open Source implementations, we have noted the
availability in Table \ref{tab:impl}. While a number of
implementations are not strictly Open Source according to OSI
definitions, the fact that they provide free academic licenses does
allow them to be used somewhat freely.

@@

As noted above, different implementations of the same descriptor can
generate slightly different values depending on the underlying
chemistry model, differences in reference values and so on. Even
within the same software implementation, different versions of the
same descriptor can generate different values. Thus to maintain
reproducibility in studies that employ molecular descriptors, some form
of versioning is crucial. The simplest form of version is to manually
note the version of the implementation used for the calculation and
report it along with the results. Though useful, it is not amenable to
automation. In some cases, toolkits will provide an API call to
retrieve the version information, which can then be associated with a
descriptor calculation.

@@

>>>>

In addition to libraries and their wrappers there are various GUI
applications that allow easy descriptor calculations. Examples include
Bioclipse \cite{Spjuth:2007aa} (see Figure~\ref{fig:tools}), MOE (Chemical Computing Group) and
Maestro (Schr\"{o}dinger, Inc.). Workflow tools are also a useful
class of applications for descriptor generation and allow one to
easily generate descriptors from multiple sources~\cite{Truszkowski2011} (see Figure~\ref{fig:tools}). Given the focus of
this article on Open Source implementations, we have noted the
availability in Table \ref{tab:impl}. While a number of
implementations are not strictly Open Source according to OSI
definitions, the fact that they provide free academic licenses does
allow them to be used somewhat freely.

@@

As noted above, different implementations of the same descriptor can
generate slightly different values depending on the underlying
chemistry model, differences in reference values and so on. Even
within the same software implementation, different versions of the
same descriptor can generate different values. Thus to maintain
reproducibility in studies that employ moleculad2a28dc0c273a4e060c2fea503adc36er descriptors, some form
of versioning is crucial. The simplest form of version is to manually
note the version of the implementation used for the calculation and
report it along with the results. Though useful, it is not amenable to
automation. In some cases, toolkits will provide an API call to
retrieve the version information, which can then be associated with a
descriptor calculation.

@@

\ctable[caption={Four tools to calculate descriptors: Bioclipse (top left), which allows selecting descriptor
implementations from various independent tools, CDK-Taverna (top right), which is an extension to Taverna
to calculate descriptors with the CDK, Ambit2 (bottom left), which implements the OpenTox API providing
a REST-based API for descriptor calculation and wraps various descriptor calculation tools,
and ....},cap={},label={fig:tools},botcap,figure]
{c}
{}
{
  \includegraphics[width=0.48\linewidth]{bioclipse}
  \includegraphics[width=0.48\linewidth]{cdktaverna} \\
  \includegraphics[width=0.48\linewidth]{ambitOnline}
}
